---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---
## Loading required packages
```{r}
require(dplyr)
require(ggplot2)
```

## Loading and preprocessing the data

When the CSV file is read in, we set *stringsasFactors* to FALSE in order to avoid unnecessary (in this case) complications caused by strings being imported as factors. We also set the classes appropriately for each column.

```{r}
# Set the correct working directory
setwd("/home/sean/DataScience/RepData_PeerAssessment1")
# Read in the data file
Data <- read.csv("activity.csv", stringsAsFactors = FALSE, colClasses=c("numeric", "Date", "numeric"))
```



## What is mean total number of steps taken per day?

We now want to calculate the total number of steps taken per day, dplyr is used to group the observations and sum them.

```{r}
stepsPerDay <- group_by(Data,date) %>%
    summarise(steps=sum(steps))
```

Now we will plot this data as a histogram - we use the Freedman-Diaconis rule to determine the bin width as that is normally pretty robust.

```{r}
hist(stepsPerDay$steps,breaks="FD", xlab="Steps/day", main="Histogram of The Number of Steps Per Day")
```

We now want to calculate the mean and median of the number of steps per day.

```{r}
mean <- mean(stepsPerDay$steps, na.rm=TRUE)
median <- median(stepsPerDay$steps, na.rm=TRUE)
```
 The mean = `r mean`  
 The median = `r median`
 
## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
